---
title: "README"
author: "Robert West"
date: "6/8/2020"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F)
knitr::opts_chunk$set(warning=F)
knitr::opts_chunk$set(message=F)
library(ggplot2)
library(jsonlite)
library(tidyverse)
library(knitr)
library(httr)
```

# Describe JSON data. What is it, where does it get used, and why is it a good way to store data? This should be detailed enough that someone that hasn’t seen JSON data would have a good idea what they are dealing with. You should link to references where applicable.



# Discuss the possible packages/functions that are available for reading JSON data into R. (There are three major packages for JSON data.) Choose one and explain why you’ve chosen it.


# PLAYING AROUND WITH THE API

You should have a function to return parsed data from the following calls:
∗ /franchise (Returns id, firstSeasonId and lastSeasonId and name of every team in the history
of the NHL)

∗ /franchise-team-totals (Returns Total stats for every franchise (ex roadTies, roadWins, etc))

∗ /site/api/franchise-season-records?cayenneExp=franchiseId=ID (Drill-down into season records for a specific franchise)
· User should be able to specify the franchise

∗ /franchise-goalie-records?cayenneExp=franchiseId=ID (Goalie records for the specified fran- chise)
· User should be able to specify the franchise


∗ /franchise-skater-records?cayenneExp=franchiseId=ID (Skater records, same interaction as goalie endpoint)
· User should be able to specify the franchise
```{r}
base_url = "https://records.nhl.com/site/api"
test_text = content(GET(url=paste0(base_url, "/franchise")), "text")
test_list = jsonlite::fromJSON(test_text, flatten=T)

str(test_list)
test_list$data

yay=test_list$data
```


```{r}
test2_text = content(GET(url=paste0(base_url, "/franchise-team-totals")), "text")
test2_list = jsonlite::fromJSON(test2_text, flatten=T)

str(test2_list)
test2_list$data
```
































